%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------

\documentclass{scrartcl}

% Move the margin to the left of the page
\reversemarginpar

% New command defining the margin text style
\newcommand{
    \MarginText}[1]{
        \marginpar{
            \raggedleft
            \itshape
            \small#1
        }
}

% Use the classicthesis style for the style of the document
\usepackage[nochapters]{classicthesis}

% Remove the date from the document's footer
\date{}

% Use the currvita style for the layout of the document
\usepackage[LabelsAligned]{currvita}

\usepackage[left=2in,right=.9in,top=.45in,bottom=.65in]{geometry}

\usepackage{xcolor}

\definecolor{myblue}{HTML}{228FC4}

% Font color of your name at the top
\renewcommand{\cvheadingfont}{
    \Large
    \color{Maroon}
}

% Required for adding links and customizing them
\usepackage{hyperref}

% Set link colors
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon}

% Set the width of the date box in each block
\newlength{\datebox}\settowidth{\datebox}{}

% Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and the position/employer/location field
\newcommand{\NewEntry}[2]{
    \noindent
    \hangindent=1em
    \hangafter=0 #1 #2
    \vspace{0.15em}
}

% Define a command for descriptions of each entry - change spacing and font sizes here
\newcommand{\Description}[1]{
    \hangindent=1em
    \hangafter=0
    \noindent
    \raggedright
    \footnotesize{#1}
    \par
    \normalsize
    \vspace{.75em}
}


%----------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------

\begin{cv}{

\hspace{-4.5em}
\centerline{
    \spacedallcaps{Brian Jacobel}}\vspace{.8em}
}

\hspace{-4.5em}
\centerline{
    \textit{email}
    \enspace
    \href{mailto:brian@bjacobel.com}{brian@bjacobel.com}
    \qquad
    \textit{portfolio}
    \enspace
    \href{http://github.com/bjacobel}{github.com/bjacobel}
    \qquad
    \textit{web}
    \enspace
    \href{http://bjacobel.com}{bjacobel.com}
}

\vspace{1em}

%----------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{\large{Education}}

\vspace{.75em}

\NewEntry{
    \kern -3pt
    \textit{September 2010 -- May 2014}
    ~~$\cdotp$~~
    Bachelor of Arts
    ~~$\cdotp$~~
    \textsc{\large Bowdoin College}
}

\Description{
    \MarginText{Bachelor of Arts}
    \kern -5pt
    \textsc{major:} Computer Science
    ~~$\cdotp$~~
    \textsc{minor:} Math
    ~~$\cdotp$~~
    \textsc{gpa:} $3.469$ \newline
    \textsc{Honors:} Sarah and James Bowdoin Scholar \\
}

\vspace{-1.5em}

\NewEntry{}{}

\Description{
    \MarginText{Selected Coursework}
    \kern -5pt
    Computer Networks
    ~~$\cdotp$~~
    Artificial Intelligence
    ~~$\cdotp$~~
    Open Source Software Development
    ~~~~
    Algorithms
    ~~$\cdotp$~~
    Independent Study in Web Development
    ~~$\cdotp$~~
    Computer and Network Security
}



%----------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------

\spacedlowsmallcaps{\large{Skills}}

\vspace{1em}

\Description{
    \MarginText{Languages}
    \kern -5pt
    Python,
    JavaScript,
    Ruby,
    Go,
    Java,
    C++,
    PHP,
    Objective-C
    (most to least proficient)
}

\vspace{-0.4em}

\Description{
    \MarginText{Web Development}
    \kern -5pt
    React,
    Redux,
    Webpack,
    AngularJS,
    Sass,
    Ruby on Rails,
    Django,
    Flask,
    Martini
}

\vspace{-0.4em}

\Description{
    \MarginText{DB \& Systems}
    \kern -5pt
    AWS EC2 \& Lambda,
    Docker,
    PostgreSQL,
    DynamoDB,
    MongoDB
}

\vspace{-0.4em}

\Description{
    \MarginText{Misc.}
    \kern -5pt
    Git,
    REST,
    TDD,
    CloudFormation,
    AWS IAM,
    Ansible,
    Responsive Web Design
}
\vspace{-0.4em}

\vspace{.75em}

%----------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{\large{Work Experience}}

\vspace{.75em}


\NewEntry{
    \kern -3pt
    \textit{June 2015 -- January 2016}
    ~~$\cdotp$~~
    \textsc{\large Localytics}
}

\Description{
    \MarginText{Software Engineer}
    \kern -5pt
    Contributed significant functionality to Localytics' analytics and marketing automation {\href{https://dashboard.localytics.com/ecommerce}{dashboard}}, a large AngularJS and Ruby on Rails codebase. Worked with a small team to ship Remarketing, a feature set which generated \$280,000 ARR in its first quarter. With the Remarketing team, led the Localytics frontend engineering team in several major technical debt reduction efforts including migration from Coffeescript to ES6 and from Sprockets to Webpack. Using ES6, React and AWS Lambda, worked with a cross-functional team to build the frontend for an internal tool that provides permissions and security for a massive-scale AWS deployment. Packaged, documented and trained others on these technologies in preparation for rolling out their use across the engineering team.
}


\vspace{.75em}


\NewEntry{
    \kern -3pt
    \textit{June 2014 -- June 2015}
    ~~$\cdotp$~~
    \textsc{\large Raizlabs}
}

\Description{
    \MarginText{Full-stack Web Developer}
    \kern -5pt
    Created responsive web applications built to client specifications using AngularJS, BackboneJS and Ruby on Rails. Developed web back-ends to power native applications using Go, Django, PostgreSQL, MongoDB, AWS and Ansible. Worked closely with members of Raizlabs' native development teams to architect, develop and review REST APIs for clients including Fortune 50 companies and innovative start-ups.
}

\vspace{.75em}

\NewEntry{
    \kern -3pt
    \textit{June -- December 2013}
    ~~$\cdotp$~~
    \textsc{\large Atlantic Media}
}

\Description{
    \MarginText{Digital Technology Intern}
    \kern -5pt
    Worked with a small, agile team of full-stack developers on the PHP and Django codebases supporting Atlantic Media's digital properties. Deployed code to {\href{http://theatlantic.com}{theatlantic.com}} and {\href{http://theatlanticwire.com}{theatlanticwire.com}} daily. Participated as a full member of the team, including code reviews and daily standups. Individually carried a number of projects to completion, including an interactive feature experienced by over 250,000 visitors. Continued working for the Atlantic as a freelance web developer through the end of 2013.
}

\vspace{.5em}

%----------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{\large{Selected Personal Projects}}

\vspace{1em}

\Description{
    \MarginText{Bongo}
    \kern -5pt
    A custom CMS and news site developed for the Bowdoin Orient, my college newspaper.
    \newline
    \textit{Using:}
    Django, Python 2/3, Ansible, AWS EC2
    \qquad
    \textit{At:}
    \href{https://github.com/bowdoinorient/bongo}{github.com/bowdoinorient/bongo}
}


\Description{
    \MarginText{Gifs}
    \kern -5pt
    A webapp for storing, sharing, tagging and searching your personal gif collection.
    \newline
    \textit{Using:}
    React, Redux, ES6, Webpack, AWS S3, DynamoDB
    \qquad
    \textit{At:}
    \href{https://github.com/bjacobel/gifs}{github.com/bjacobel/gifs}
}


\Description{
    \MarginText{BosFoodFails}
    \kern -5pt
    A Twitter bot that tracks health inspection violations in Boston restaurants.
    \newline
    \textit{Using:}
    Python, AWS Lambda, DynamoDB, KMS
    \qquad
    \textit{At:}
    \href{https://github.com/bjacobel/bosfoodfails}{github.com/bjacobel/bosfoodfails}
}

\Description{
    \kern -5pt
    More at \href{https://bjacobel.com/projects}{bjacobel.com/projects}
}


\end{cv}

\end{document}
